Self Regulation Ontology Retest Data Report

### 2018-01-18 code/SRO_Report.Rmd
updating report for draft

ggsave('Variance_Breakdown_Plot.jpg', plot = p3, device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures", width = 24, height = 20, units = "in", dpi = 100)
rm(tmp, labels)
```

@@

That said this kind of analysis seems too in the weeds for a paper that is trying to give a global sense of the differences between self-regulation measures in their suitablity for individual difference analyses based on their stability across time. Such analyses would provide a detailed examination of how to extract the most reliable/best individual difference measure from tasks with a set of mediocre variables to begin with. So I am choosing to ignore this for now but this can be revisited.

NOTE: DO THIS ON AN EXAMPLE TASK AND LEAVE TO THE READER TO DO

>>>>

ggsave('Variance_Breakdown_Plot.jpg', plot = p3, device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures", width = 24, height = 20, units = "in", dpi = 100)
rm(tmp, labels, p1, p2 , p3)
```

@@

These kinds of analyses are too task-specific and in-depth for a paper that is trying to give a global sense of the differences between self-regulation measures in their suitablity for individual difference analyses based on their stability across time. Such analyses would provide a detailed examination of how to extract the most reliable/best individual difference measure from tasks with a set of mediocre variables to begin with. Though we do not provide such a comprehensive analysis of this sort in this paper we provide a single example of this approach and hope the open access we provide to the data spurs further work.

For this example we look at the retest reliability of the ... measures from the ... task with ... trials. Here is a graph of how the point estimates of the retest reliability changes for each of the dependent measures using different numbers of trials to estimate them.

target task: one without hddm variables, has dv's that are easily codable in r, a lot of trials, possibly multiple dependent measures
method: import raw response data for chosen task for both t1 and t2, calculate dv's for for both t's for different number of trials, calculate retest reliability point estimates for each of these dv's with different trial numbers
candidates: angling risk task, columbia card task, dietary decision, hierarchical rule, keep track, probabilistic selection, psychological refractory period, two stage decision

```{r}
#read t1 data
t1_hr = read.csv(gzfile('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Complete_01-15-2018/Individual_Measures/hierarchical_rule.csv.gz', 'rt'))

t2_hr = read.csv(gzfile('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_11-27-2017//Individual_Measures/hierarchical_rule.csv.gz', 'rt'))

#get only retest subjects
t1_hr = t1_hr[as.character(t1_hr$worker_id) %in% as.character(test_data$sub_id),]
t2_hr = t2_hr[as.character(t2_hr$worker_id) %in% as.character(retest_data$sub_id),]

#remove missed trials (rt == -1)
t1_hr = t1_hr %>% filter(rt != -1)
t2_hr = t2_hr %>% filter(rt != -1)

#dv's
#accuracy: mean correct
#average rt: median of correct trials only
#score: sum correct

calc_break_dvs = function(x, breaks=seq(0, 360, 10)[-1]){
  out = data.frame()
  for(i in 1:length(breaks)){
    tmp = x[1:breaks[i],]
    dvs = tmp %>%
      summarise(acc = mean(correct),
                avg_rt = median(rt[correct == 1]),
                score = sum(correct))
    out = rbind(out, dvs)
  }
  return(out)
}

tmp = t1_hr%>% filter(worker_id == 's005')

calc_break_dvs(tmp)

t1_hr %>%
  group_by(worker_id) %>%
  summarise(acc = mean(correct),
                avg_rt = median(rt[correct == 1]),
                score = sum(correct))
```
